\documentclass[11pt, norsk, a4paper]{article}
\usepackage{charter,graphicx}

\usepackage{geometry}
\geometry{legalpaper, margin=1in}

\renewcommand{\baselinestretch}{1.2}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{wrapfig}
\setlength{\parindent}{0in}
\usepackage{caption}
\usepackage{braket}
\usepackage{nccmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{listings}
\usepackage[makeroom]{cancel}
\usepackage{xcolor}

\newcommand\norm[1]{\lVert#1\rVert}
\newcommand\inner[1]{\langle#1\rangle}

\title{Minimazation problem}
\author{m.kristiansen}
\date{\today}

\begin{document}

\maketitle

\subsubsection*{Proposition}
Let $A$ and $B$ be Hilbert spaces, and $u \in A, v\in B$ then the cartiesian product of $A$ and $B$ denoted 
$$V = A\times B$$
is also a Hilbert space equipped with the inner product 
\begin{align*}
    \inner{(u,v), (u,v)}_V = \inner{u,u}_{H^1}+\inner{v,v}_{H^1}
\end{align*}
where $(\cdot, \cdot)$ denotes a pair of functions and $\inner{\cdot, \cdot}$ the inner product. We also have the norm
\begin{align*}
    \norm{(u,v)}^2_V = \norm{u}^2_{H^1}+\norm{v}^2_{H^1}
\end{align*}
\begin{proof}
    insert reference or add proof.
\end{proof}


We define the the energy functional 
\begin{align*}
    F(u,\hat{u}) = \frac{1}{2}\int_\Omega (Du)^2 d\Omega + \frac{1}{2}\int_{\Gamma}(D\hat{u})^2 d\Gamma + \frac{\gamma}{2}\int_{\Gamma} (u-\hat{u})^2 d\Gamma
\end{align*}
for $\gamma > 0$ and consider the following minimazation problem 
\begin{align*}
    \min_{(u,\hat{u}) \in X} F(u,\hat{u})
\end{align*}

A minimum $(u, \hat{u})$ is characterized by $F(u, \hat{u}) \leq F(u+\epsilon v, \hat{u}+\epsilon \hat{v}) $ for all $v, \hat{v} \in Y$ and $\epsilon > 0$. $X, Y$ denotes function spaces which will be decided later. Defining a new function 
\begin{align*}
    \Phi(\epsilon) = F(u+\epsilon v, \hat{u}+\epsilon \hat{v})
\end{align*}
still requiring $\epsilon > 0$, we know that $\Phi$ has a minimum at $\epsilon = 0$ and 
$
\frac{d\Phi(\epsilon)}{d\epsilon} |_{\epsilon =0 } = 0.
$
Whence, 
\begin{align*}
    \frac{dF(u+\epsilon v, \hat{u}+\epsilon\hat{v})}{d\epsilon} = \int_\Omega (Du+\epsilon Dv)\cdot Dv+\int_\Gamma (D\hat{u}+\epsilon D\hat{v})\cdot D\hat{v} + \gamma \int_\Gamma (u+\epsilon v -(\hat{u}-\hat{v}))\cdot (v-\hat{v})
\end{align*}
Setting $\epsilon = 0$ we obtain the variational form. 
\begin{align*}
   B[(u,\hat{u}), (v, \hat{v})] &= a(u, v) + b(\hat{u}, \hat{v}) + c((u,v), (\hat{u},\hat{v}))  \\
   &=   \int_\Omega Du\cdot Dv +\int_\Gamma D\hat{u}\cdot D\hat{v} +\gamma \int_\Gamma (u-\hat{u})(v-\hat{v})
\end{align*}
We define $V, \hat{V} = H^1_0(\Omega)\times H^1_0(\Gamma)$ where $V$ detones the trial space and $\hat{V}$ the test space. Additonally we equip the spaces with the norm $\norm{(u,\hat{u})}^2_V = \norm{u}_{H^1(\Omega)}^2+\norm{\hat{u}}_{H^1(\Gamma)}^2$. 
Our variational formulation is thus, find $(u,\hat{u}) \in X$ such that 
\begin{align*}
    B[(u, \hat{u}), (v, \hat{v})] = l[(v, \hat{v})] 
\end{align*}
holds for all $(v, \hat{v}) \in Y$. From (Poisson, paper) we know that the natural spaces are $u, v \in H^1_0(\Omega)$ and $\hat{u}, \hat{v} \in H^1_0(\Gamma)$ whence, $X = Y = H^1_0(\Omega) \times H^1_0(\Gamma)$.  Lax-Milgrams theorem ensures existence of unique $(u,\hat{u}) \in X$ if the bilinear operator is bounded and elliptic and $l: \hat{V} \to \mathbb{R}$ is a bounded linear functional on $Y$. 
\ 
To show boundedness, we recall that $\norm{u}^2_{H^1} = \norm{u}^2_{L^2} + \norm{Du}^2_{L^2}$ and the Cauchy-Schwartz inequality 
\begin{align*}
    \int |uv| \leq \norm{u}_{L^2}\norm{v}_{L^2}
\end{align*}
Whence, 
\begin{align*}
    |B(\vec{u}, \vec{v})| &\leq \norm{Du}_{L^2}\norm{Dv}_{L^2}+ \norm{D\hat{u}}_{L^2}\norm{D\hat{v}}_{L^2} \\ &+\gamma\Bigr[\norm{u}_{L^2}\norm{v}_{L^2}+\norm{u}_{L^2}\norm{\hat{v}}_{L^2}+\norm{\hat{u}}_{L^2}\norm{v}_{L^2}+\norm{\hat{u}}_{L^2}\norm{\hat{v}}_{L^2}\Bigr] \\
    & \leq \norm{u}_{H^1}\norm{v}_{H^1}+ \norm{\hat{u}}_{H^1}\norm{\hat{v}}_{H^1} \\ &+\gamma\Bigr[\norm{u}_{H^1}\norm{v}_{H^1}+\norm{u}_{H^1}\norm{\hat{v}}_{H^1}+\norm{\hat{u}}_{H^1}\norm{v}_{H^1}+\norm{\hat{u}}_{H^1}\norm{\hat{v}}_{H^1}\Bigr] \\
    &= (1+\gamma) \norm{u}_{H^1}\norm{v}_{H^1}+(1+\gamma)\norm{\hat{u}}_{H^1}\norm{\hat{v}}_{H^1}+\gamma(\norm{u}_{H^1}\norm{\hat{v}}_{H^1}+\norm{\hat{u}}_{H^1}\norm{v}_{H^1}) \\
    &\leq (1+\gamma) \Bigr[\norm{u}^2+\norm{v}^2+\norm{\hat{u}}^2+\norm{\hat{v}}^2\Bigr]\\
    & = (1+\gamma)\norm{\vec{u}}_X\norm{\vec{v}}_X
\end{align*}
Where in the last inequality we used Young's inequality with $p = q = 2$. \
To show ellipticity we recall Poincare's inequality 
\begin{align*}
    \norm{u}_{L^2} \leq C\norm{Du}_{L^2}
\end{align*}
Which also implies 
\begin{align*}
 \norm{u}^2_{H^1} \leq 2C^2\norm{Du}^2_{L^2}
\end{align*}
Where the constant $C$ depends on the geometry of the domain(s). 
The bilinear operator is thus bounded below by 
\begin{align*}
    B[\vec{u}, \vec{u}] &= \int_{\Omega} |Du|^2 +\int_\Gamma|D\hat{u}|^2+\gamma \int_\Gamma |u-\hat{u}|^2 \\
   & \geq \int_{\Omega} |Du|^2 +\int_\Gamma|D\hat{u}|^2 \\
   & \geq \frac{1}{2C^2} \Bigr[\norm{u}_{H^1}^2+\norm{\hat{u}}_{H^1}^2\Bigr]\\
   & =  \frac{1}{2C^2} \norm{\vec{u}}_X^2 
\end{align*}

\subsubsection*{Cea's lemma} 
Suppose the conditions for the Lax-Milgram theorem and that $\alpha$ and $\beta$ denotes the constant obtained from the lower and upper bound of the bilinear form. (ellipticity and boundedness). Furthermore, consider the same problem on a finite dimensional subspace $X_h \subset X$ with the unique solution $\vec{u}_h$. Then we have the estimate 
\begin{align}
    \norm{\vec{u}-\vec{u}_h}_X \leq \frac{\beta}{\alpha}\norm{\vec{u}-\vec{v}}_X
\end{align}
for all $\vec{v} \in Y$. \\
We have 
\begin{align*}
    \norm{\vec{a}-\vec{b}}^2_X = \norm{(a_1, a_2) - (b_1, b_2)}^2_X = \norm{(a_1-b_1, a_2-b_2}^2_X = \norm{a_1-b_1}_{H^1}^2+\norm{a_2-b_2}^2_{H^1}
\end{align*}
Hence, we can rewrite (1) as 
\begin{align*}
    \norm{u-u_h}^2_{H^1}+\norm{\hat{u}-\hat{u_h}}^2_{H^1} \leq \frac{\beta^2}{\alpha^2}\bigr[ \norm{u-v}^2_{H^1}+\norm{\hat{u}-\hat{v}}^2_{H^1}\bigr] 
\end{align*}
Inserting our estimates for $\alpha$ and $\beta$ we obtain 
\begin{align}
    \norm{u-u_h}^2_{H^1}+\norm{\hat{u}-\hat{u_h}}^2_{H^1} \leq 4C^4(1+\gamma)^2\bigr[ \norm{u-v}^2_{H^1}+\norm{\hat{u}-\hat{v}}^2_{H^1}\bigr] 
\end{align}







\end{document}